---
title: "Stat 108: Lab 4"
author: "Dylan Scoble"
date: "2/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(broom)
```


### Exercise 1
There are 1,258 observations in the new dataset, after we filter for observations that have a carat weight of 0.5.
```{r}
data <- diamonds %>% 
  filter(carat == 0.5)
glimpse(data)
```


### Exercise 2
As shown in the histogram, the two levels of cut with the smallest number of observations are "few" and "good".

```{r}
ggplot(data = data, aes(x = cut)) +
  geom_bar() +
  labs(title = "Histogram of Cut")
```

### Exercise 3
```{r}
lumpeddata <- data %>%
  mutate(cut = fct_lump_n(cut, n=3))

ggplot(data = lumpeddata, aes(x = cut)) +
  geom_bar() +
  labs(title = "Histogram of Cut")
```

### Exercise 4
```{r}
plot <- ggplot(data = lumpeddata, aes(x = cut, y = price)) +
  geom_boxplot() +
  labs(title = "Relationship between Price and Cut",
       x = "Cut",
       y = "Price")

plot
```


### Exercise 5
The output of this code is a table that shows the mean, standard deviation, and number of observations of price for each category of cut.
```{r}
lumpeddata %>%
  group_by(cut) %>% 
  summarise(mean = mean(price),
            std_dev = sd(price),
            num_observations = n()
  )
```

### Exercise 6
For Diamonds that are 0.5 carats, there is a minor linear relationship between cut and price. As cut increases from less than very good, to very good, to premium, to ideal, the mean price of that category also increases.


